Restrictive Clearance Comparison

### 2024-03-27 data-raw/RestrictiveClearance_comparison.Rmd
Preparation for implementation of static restrictive vs non-restrictive total clearance models

common_chems[!(common_chems %in% get_cheminfo(info = "DTXSID", model = "pbtk"))] %>% unique() %>% sort()
```

@@

@@

>>>>

common_chems[!(common_chems %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk"))] %>%
  unique() %>%
  sort()
```

@@

hep_clearance_df <- data.frame(Chemical = common_chems) %>%
  rowwise() %>%
  mutate(Restrict_Cl = calc_hep_clearance(dtxsid = Chemical,
                                            restrictive.clearance = TRUE,
                                            suppress.messages = TRUE),
         nonRestrict_Cl = calc_hep_clearance(dtxsid = Chemical,
                                            restrictive.clearance = FALSE,
                                            suppress.messages = TRUE)) %>%
  ungroup()

@@

Finally, what I want to analyze is how good the fits for these chemicals are relative to the rest of the chemicals.

```{r fit_analysis}
wm <- get_winning_model(my_pk)
ingroup_rmse <- rsq(my_pk) %>% inner_join(wm) %>%
  filter(Chemical %in% combined_clearance_df$Chemical) %>%
  mutate(Group = "in httk")

outgroup_rmse <- rsq(my_pk) %>% inner_join(wm) %>%
  filter(!(Chemical %in% combined_clearance_df$Chemical)) %>%
  mutate(Group = "not in httk")

all_group_rmse <- bind_rows(ingroup_rmse, outgroup_rmse)

all_group_rmse %>%
  filter(Species == "rat") %>%
  ggplot(aes(x = Rsq, y = Chemical,
             shape = Group)) +
  geom_point() +
  facet_grid(rows = vars(Group), scales = "free", space = "free") +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        legend.direction = "vertical",
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text.y = element_blank())

ggsave(paste0(Sys.getenv("FIG_DIR"), "Rsq_gaspbtk.png"),
       height = 5,
       width = 5)

## Exploring _httk_ parameters and solved values for `gas_pbtk`

```{r httk_solution}
httk::calc_tkstats(dtxsid = unique(combined_clearance_df$Chemical)[[5]])
httk::parameterize_gas_pbtk(restrictive.clearance = TRUE,
                            dtxsid = unique(combined_clearance_df$Chemical)[[5]])

httk::solve_gas_pbtk(dtxsid = unique(combined_clearance_df$Chemical)[[5]],
                     parameters = httk::parameterize_gas_pbtk(
                       restrictive.clearance = TRUE,
                       dtxsid = unique(combined_clearance_df$Chemical)[[5]]
                       ),
                     dose = 10,
                     exp.conc = 0,
                     input.units = "mg",
                     output.units = "mg",
                     days = 3,
                     plots = TRUE)
